---
title: 'Project 2: EDA'
author: "Jaclyn A Coate"
date: "3/23/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r environment prep}
library(tidyverse)
library(data.table)
library(mice)
library(skimr)
library(corrplot)
library(cowplot)
```

```{r data prep}
bankraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_2/master/Data/bank-additional-full.csv", header = TRUE, sep = ";", strip.white = TRUE)
str(bankraw)
head(bankraw)
```

# Question of Interest:
- The data is related with direct marketing campaigns (phone calls) of a Portuguese banking institution. The classification goal is to predict if the client will subscribe a term deposit (variable y).

## EDA to determine narrow down variables to use for the Logistic Regression model

#### Properly naming response variable

```{r}
setnames(bankraw, "y", "Subscription")
```

#### Removing logically irrelevant variables
- Upon reviewing the variables and their accompanying descriptions we have decided to remove 'duration'. This is due to the fact that the time duration of a call would be a post performance metric that would not be something known in advance (before the subscription would or would not take place). 

```{r drop irrelevant variables}
str(bankraw)
#Dropping logical irrelevant variables: "duration"
bankraw2 <- select(bankraw, -c("duration"))
head(bankraw2)
invisible(view(bankraw2))
```

#### NA Evaluation and Drop

```{r NA eval}
#Checking for NAs
md.pattern(bankraw2)
#Results show no NAs
```

#### Zero variance variable check - all show variance so remain in model

```{r zero variable check}
skim(bankraw2)
```

#### Continuous Variable Review
- First we will review all continuous variables and see whic of those are the most associated with our categorical variable.
  - To accomplish this we will create boxplots of the individual continuous variables compared to the categorical response variable and look for large differences in the summary statistic ranges for the categorical variables.

```{r Subscription v Age}
plot(bankraw2$Subscription, bankraw2$age, xlab = "Subscription", ylab = "Age", title = "Subscription v Age", col=c(82,107)) 
```

```{r Subscription v Campaign}
#Upon review of the intial boxplot we see outlier that are preventing us from seeing the actual boxplot shape and move
plot(bankraw2$Subscription, bankraw2$campaign, xlab = "Subscription", ylab = "Campaign", title = "Subscription v Campaign", col=c(82,107)) 

#We drop all campaigns values >6 in an attempt to see the graph more clearly
campOutliers <- bankraw2[!(bankraw2$campaign > 6),]
invisible(campOutliers)
plot(campOutliers$Subscription, campOutliers$campaign, xlab = "Subscription", ylab = "Campaign < 25", title = "Subscription v Campaign < 25", col=c(82,107)) 
```

```{r Subscription v pdays}
#Upon further review of this variable we are going to move forward with created a new variable that is 'Contacted' or 'Not Contacted' and evaluate as a categorical variable against 'Subscriptions'. This will be done in objective 1, but for now in the EDA we will leave as numeric.
plot(bankraw2$Subscription, bankraw2$pdays, xlab = "Subscription", ylab = "pdays", title = "Subscription v cons.conf.idx", col=c(82,107)) 

#In order to evaluate as numeric dropping outliers of 999 and regraphing the pdays numeric variable.
pdaysOutliers <- bankraw2[!(bankraw2$pdays == 999),]
invisible(pdaysOutliers)

plot(pdaysOutliers$Subscription, pdaysOutliers$pdays, xlab = "Subscription", ylab = "pdays", title = "Subscription v cons.conf.idx", col=c(82,107)) 
```

```{r Subscription v previous}
plot(bankraw2$Subscription, bankraw2$previous, xlab = "Subscription", ylab = "cons.conf.idx", title = "Subscription v cons.conf.idx", col=c(82,107)) 
```

```{r Subscription v cons.conf.idx}
plot(bankraw2$Subscription, bankraw2$cons.conf.idx, xlab = "Subscription", ylab = "cons.conf.idx", title = "Subscription v cons.conf.idx", col=c(82,107)) 
```

```{r Subscription v cons.price.idx}
plot(bankraw2$Subscription, bankraw2$cons.price.idx, xlab = "Subscription", ylab = "cons.price.idx", title = "Subscription v cons.price.idx", col=c(82,107)) 
```

```{r Subscription v emp.var.rate}
plot(bankraw2$Subscription, bankraw2$emp.var.rate, xlab = "Subscription", ylab = "cons.conf.idx", title = "Subscription v emp.var.rate", col=c(82,107)) 
```

```{r Subscription v euribor3m}
plot(bankraw2$Subscription, bankraw2$euribor3m, xlab = "Subscription", ylab = "euribor3m", title = "Subscription v euribor3m", col=c(82,107)) 
```

```{r Subscription v nr.employed}
plot(bankraw2$Subscription, bankraw2$nr.employed, xlab = "Subscription", ylab = "nr.employed", title = "Subscription v nr.employed", col=c(82,107)) 
```

- An additional way to view which continuous variables are highly likely to influence the dependent variable is through density plots. The below function runs density plots for every continuous variable that is from above and anywehre there are spikes that are highly separated we know it is probable it will influence the dependent variable.

```{r density curves}
densityPlots <- function(df, explanatory, response){
df %>% ggplot(aes_string(x = explanatory, fill = response)) + geom_density(alpha=0.5)
}
densityPlotsList <- lapply(bankraw2 %>% keep(is.numeric) %>% colnames, function(x) densityPlots(bankraw2, x, "Subscription"))
for(i in densityPlotsList){
  print(i)
}
#Testing to see if function above works properly
#densityPlots(bankraw2, "age", "Subscription")
```

##### Continuous Variable Removal
#- As we can see from the above boxplots the continuous variable ranges for the Yes and No outcomes of the #subscription do not greatly differ. Once could argue that 

#```{r removal of all continuous variables}
bank3 <- select(bankraw2, -c("nr.employed", "euribor3m", "emp.var.rate", "cons.price.idx", "cons.conf.idx"))
#```

#### Continuous Variable Multicollinearity Check
- Multicollinearity will weaken the model
- At first glance there does seem to be some correlation between a few of the continuous variables
- When highlighting the yes versus no result for signing up, we cannot see a clear separation of anykind. This will lead us away from utilizing the principal componenet analysis technique for variable selection

- The below pairs graphs shows us the separation of Yes and No results of the dependent variable by graph. We can observe that there is no clear separation and therefore PCA would not be a good variable reduction tool moving forward. So we continue with a standard EDA.

```{r pairs graph}
view(bankraw2)
#Reducing to only continuous variables and graphing by continuous variables, then colored by response in order to determine if there is separation of results and the ability to utilzie PCA
bankraw2 %>% keep(is.numeric) %>% pairs(,col=bankraw2$Subscription)
```

- To additionally conintue to check multicollinearity we run a correlation matrix
  - Using the correlation matrix we can much more clearly see highly correlated variables in blue and orange gradient
  
```{r correlation matrix}
#Plot numeric variables v numeric variables
bankraw2 %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", 
                                                   order="hclust", tl.srt=45, tl.cex = 0.8)
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
bank3 <- select(bankraw2, -c("pdays", "euribor3m", "nr.employed", "emp.var.rate", "age"))
skim(bank3)
```

- After reviewing the need to remove the below variables is clear. Due to their correlation with eachother, they could weaken our model
  - "euribor3m", "nr.employed", "emp.var.rate"
- Additionally, seeing the "pdays" and previous are highly correlated we choose to remove "pdays" since we think this will be more useful as a categorical variable in Object 2
- Lastly, we see that "age" has no true significance on the indepenent variable. Removing as well.
- See correlation matrix below after correlated continuous variables have been removed

```{r correlation matrix 2}
#Plot numeric continuous variables to double check all correlated values have been removed
bank3 %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
```

#### Categorical Variable Review

```{r Categorical Variable Review Grid}
# 1. Name target variable
#targetCatCat <- "Subscription"

# 2. Name explanatory variable
#explanatory <- bank3 %>% keep(is.factor) %>% colnames

# 3. Create function
numCatCat <- function(df, explanatory, response) {
  ggplot(data = df) +geom_bar(aes_string(x = explanatory, fill = response), position = "fill", alpha = 0.9) + coord_flip() #+ xlab(explanatory)
}

#  # 3a. Example of working function above
#  # numCatCat(bank3, explanatory = "education", response = "Subscription")


# 4. Create plot list for plot_grid function to reference
#plotlistCatCat <- lapply(explanatory, function(x) numCatCat(bank3, x, targetCatCat))

# 5. Grid of all categorical variables plotted against y = Subscription
#plot_grid(plotlist = plotlistCatCat)
```

- Singular break downs of the above function

```{r review data}
head(bank3)
```

```{r Job v Subscription}
numCatCat(bank3, explanatory = "job", response = "Subscription")
```

```{r Martial v Subscription}
numCatCat(bank3, explanatory = "marital", response = "Subscription")
```

```{r Education v Subscription}
numCatCat(bank3, explanatory = "education", response = "Subscription")
```

```{r Default v Subscription}
numCatCat(bank3, explanatory = "default", response = "Subscription")
```

```{r House v Subscription}
numCatCat(bank3, explanatory = "housing", response = "Subscription")
```

```{r Loadn v Subscription}
numCatCat(bank3, explanatory = "loan", response = "Subscription")
```

```{r Month v Subscription}
numCatCat(bank3, explanatory = "month", response = "Subscription")
```

```{r Day of Week v Subscription}
numCatCat(bank3, explanatory = "day_of_week", response = "Subscription")
```

```{r Poutcome v Subscription}
numCatCat(bank3, explanatory = "poutcome", response = "Subscription")
```

- Upon reviewing all of the Categorical variables we can clearly remove the below variables
  - marital, housing, loan, day_of_week
- While the below variables seem to show strong correlation with the response variable
  - job, eduction, default, month, poutcome

```{r removal of unrelated categorical variables}
bank4 <- select(bank3, -c("marital", "housing", "loan", "day_of_week"))
```

#### Summary Check on Variables

```{r summary of variables}
summary(bank4)
```

#### Export data set for simple logistic analysis 

```{r}
write.csv(bank4, file="/Users/Jaco/Desktop/SMU/Spring2020/DS_6372_Applied_Statistics/Project.2/Data/modelingdata.csv")
```