---
title: 'Project 2: EDA'
author: "Branum Stephan"
date: "3/23/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r environment prep}
library(tidyverse)
library(data.table)
library(mice)
library(skimr)
library(corrplot)
library(cowplot)
```

```{r data prep}
bankraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_2/master/Data/bank-additional-full.csv", header = TRUE, sep = ";", strip.white = TRUE)
str(bankraw)
head(bankraw)
tail(bankraw)
```

# Question of Interest:
- The data is related with direct marketing campaigns (phone calls) of a Portuguese banking institution. The classification goal is to predict if the client will subscribe a term deposit (variable y).

## EDA to determine narrow down variables to use for the Logistic Regression model

#### Properly naming response variable

```{r}
setnames(bankraw, "y", "Subscription")
colnames(bankraw)
```

#### Removing logically irrelevant variables
- Upon reviewing the available metrics, there are certain variabels that would not make logical sense as a contribution to creating a logisitc regression model

```{r drop irrelevant variables}
str(bankraw)
#Dropping logical irrelevant variables: "contact", "campaign", "pdays", "previous"
bankraw2 <- select(bankraw, -c("pdays", "previous", "contact", "campaign"))
head(bankraw2)
view(bankraw2)
```

#### NA Evaluation and Drop

```{r NA eval}
#Checking for NAs
md.pattern(bankraw2)
#Results show no NAs
```

#### Zero variance variable check - all show variance so remain in model

```{r zero variable check}
skim(bankraw2)
```

#### Continuous Variable Multicollinearity Check
- Multicollinearity will weaken the model
- At first glance there does seem to be some correlation between a few of the continuous variables
- When highglighting the yes versus no result for signing up, we cannot see a clear separation of anykind. This will lead us away from utilizing the principal componenet analysis technique for variable selection

```{r pairs graph}
view(bankraw2)
#Reducing to only continuous variables and graphing by continuous variables, then colored by response in order to determine if there is separation of results and the ability to utilzie PCA
bankraw2 %>% keep(is.numeric) %>% pairs(,col=bankraw2$Subscription)
```
```{r pca}
# find the PCA
pcaBank <- prcomp(bankraw2 %>% keep(is.numeric), center = TRUE, scale = TRUE)
summary(pcaBank)

# create scatterplot of PCA, colored by Subscription
pcaDf <- data.frame(pcaBank$x)
cbind(bankraw2, pcaDf) %>% ggplot(aes(x=PC1, y=PC2, color=Subscription, shape=Subscription)) + scale_shape_manual(values=c(1, 18)) + geom_point(alpha = 0.75) + ggtitle("PCA Plot - Colored by Subscription")
```


- To additionally check we will run a correlation matrix
  - Using the correlation matrix we can much more clearly see high correlation
    - cons.price.idx : nr.employed
    - cons.price.idx : emp.var.rate
    - cons.price.idx : euribor3m
    - nr.employed : emp.var.rate
    - nr.employed : euibor3m
    - emp.var.rate : euribor3m

```{r density curves}

densityPlots <- function(df, explanatory, response){
df %>% ggplot(aes_string(x = explanatory, fill = response)) + geom_density(alpha=0.5)
}

densityPlotsList <- lapply(bankraw2 %>% keep(is.numeric) %>% colnames, function(x) densityPlots(bankraw2, x, "Subscription"))

for(i in densityPlotsList){
  print(i)
}

#densityPlots(bankraw2, "age", "Subscription")

```

```{r correlation matrix}
#Plot numeric variables v numeric variables
bankraw2 %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
```

```{r attrition: removing highly correlated variable}
#Removing reviews_per_month due to high correlation of is and number_of_reviews
bank3 <- select(bankraw2, -c("cons.price.idx", "nr.employed", "emp.var.rate"))
skim(bank3)
```

- AFter reviewing the need to remove the below variables is clear
  - "cons.price.idx", "nr.employed", "emp.var.rate"
- See correlation matrix below after correlated continuous variables have been removed

```{r correlation matrix 2}
#Plot numeric continuous variables to double check all correlated values have been removed
bank3 %>% keep(is.numeric) %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
```

- Seeing highly correlated variables we are going to use PCA in order which numeric variables should be leveraged for our logistic regression


#### Categorical Variable Review

```{r Categorical Variable Review Grid}
# 1. Name target variable
targetCatCat <- "Subscription"

# 2. Name explanatory variable
explanatory <- bank3 %>% keep(is.factor) %>% colnames

# 3. Create function
numCatCat <- function(df, explanatory, response) {
  ggplot(data = df) +geom_bar(aes_string(x = explanatory, fill = response), position = "fill", alpha = 0.9) + coord_flip() + xlab(explanatory)
}

  # 3a. Example of working function above
  # numCatCat(bank3, explanatory = "education", response = "Subscription")


# 4. Create plot list for plot_grid function to reference
plotlistCatCat <- lapply(explanatory, function(x) numCatCat(bank3, x, targetCatCat))

# output plots in a loop
for(i in plotlistCatCat){
  print(i)
}

```

- Singular break downs of the above function

```{r review data}
head(bank3)
```

- Upon reviewing all of the Categorical variables we can clearly remove the below variables
  - marital, housing, loan, day_of_week
- While the below variables seem to show strong correlation with the response variable
  - job, eduction, default, month, poutcome

```{r removal of unrelated categorical variables}
bank4 <- select(bank3, -c("marital", "housing", "loan", "day_of_week"))
```

#### Summary Check on Variables

```{r summary of variables}
summary(bank4)
write.csv(bank4, "/Users/michaelstephan/Desktop/SMU/spring 2020/Applied Statistics/Project 2/6372_Project_2/Data/bank-model input-no continuous.csv")
```