---
title: "LDA for Objective.2"
author: "Jaclyn A Coate"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(MASS)
library(mvtnorm)
library(skimr)
library(ggthemes)
library(caret)
library(plotly)
```

```{r important test and train sets}
banktrain <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_2/master/Data/Training_Test_Splits/banktrain_raw.csv", header = TRUE, sep = ",", strip.white = TRUE)

banktest <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_2/master/Data/Training_Test_Splits/banktest_raw.csv", header = TRUE, sep = ",", strip.white = TRUE)
```

```{r review imported data}
skim(banktrain)
nrow(banktrain)

skim(banktest)
nrow(banktest)
```

#### Upon completion of our first EDA we will resume the EDA in order to accomplish an LDA model
- A LDA does not deal with categorical varaibles as predictors. Therefore we will remove the categorical variables from our train data set
  - Including removal of duration since it is considered a post variable and not a pre variable for prediction
  - Will only include continuous variables found from initial EDA

```{r categorical variable reduction}
#Remove categorical predictors
banktrain2 <- dplyr::select(banktrain, -c("age", "duration", "job", "marital", "education", "default", "housing", "loan", "contact", "month", "day_of_week", "poutcome"))
banktrain3 <- dplyr::select(banktrain2, -c("pdays", "nr_employed", "emp_var_rate", "row", "previous", "campaign"))
skim(banktrain3)
invisible(view(banktrain3))
```

### Paris Scatter Plot
- Pairs scatter plot to see if there is any separation
  - We don't see a lot so we break up the data set for larger visualizations
```{r pairs scatterplot to see separation}
banktrain3 %>% pairs(,col=banktrain3$Subscription)
```

### LDA

```{r lda}
mylda <- lda(Subscription~.,data=banktrain3)
#Predictions can come in many forms, the class form provides the categorical level of your response
Pred <- predict(mylda,newdata = banktest)$class

Truth <- banktest$Subscription
x <- table(Pred,Truth) #Creating confusion matrix
x
#Confusion matrix function
CMlda <- confusionMatrix(Pred,Truth)
CMlda
```

### QDA

```{r qda}
myqda <- qda(Subscription~.,data=banktrain3)
#Predictions can come in many forms, the class form provides the categorical level of your response
PredQ <- predict(myqda,newdata = banktest)$class

TruthQ <- banktest$Subscription
x <- table(PredQ,TruthQ) #Creating confusion matrix
x

CMqda <- confusionMatrix(PredQ, TruthQ)
CMqda
```

### 3D Graph of Continuous Variables (predictors) colored by Subscription (dependent variable)

```{r 3D graph}
fig <- plot_ly(banktrain, x= ~cons_price_idx, y= ~cons_conf_idx, z= ~euribor3m, color = ~Subscription, colors = c('#BF382A', '#228B22'))
fig2 <- fig %>% add_markers()
fig3 <- fig2 %>% layout(scene = list(xaxis = list(title = 'Consumer Price Indx'),
                     yaxis = list(title = 'Consumer Confidence Indx'),
                     zaxis = list(title = '3 Month Rate')))
fig3
```